---
title: My dynamic report 
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body { 
 font-family: Arial; 
 background-color:#121212;
 color:#ECEFF4
 }
h2 {
  color:#ECEFF4;
}
```

## Inside Your Screen: Phone Usage Behaviour Analysis 

This report analyses observational data on phone usage behaviour. Each entry represents a single phone usgae session, including duration, intention and purpose. The aim is to identify patterns in how and why people use phones.  

```{r}
library(tidyverse)

# Load dataset from published Google Sheets CSV
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRHjK6U69tunQ4OQMxnbVQ6IXGCVxU3PWlw2RzgzQYsOWOHr-tUauL5lDRaGs-hZNuZGhVMlasP3_UT/pub?gid=84486311&single=true&output=csv")
latest_data <- logged_data %>%
  rename(gender = 3, 
         phone = 4, 
         phone_use_session = 5, 
         purpose = 6, 
         intention = 7)
```

# ===== DATA EXPLORATION =====

```{r, fig.width= 14}
# Top 3 longest phone use sessions 
most_phone_use <- latest_data%>%
  arrange(desc(phone_use_session))

# as again 
most_phone_use <- most_phone_use%>% 
  slice(c(1,2,3))
num_of_rows <- length(latest_data$phone_use_session)
  
intention <- unique(most_phone_use$intention)

# purpose of top 3 phone uses 

 
# ===== FINAL CODE FOR REPORT =====

# mean of phone use duration 
mean_duration <- mean(latest_data$phone_use_session)


# average duration by purpose 
avg_by_purpose <- latest_data %>% 
  group_by(purpose) %>% 
  summarise(avg_duration = mean(phone_use_session, na.rm = TRUE))

```

There are `r num_of_rows` daily phone use reports in this data

The mean of phone use session is `r mean_duration` mins.

`r intention[1]` and `r intention[2]`  was one of the intentions of the top 3 phone uses.

# ===== BAR CHARTS =====

```{r}

#bar chart 1: count of phone use by purpose 
ggplot(latest_data, aes(x = purpose)) + 
  geom_bar(fill= "purple") + labs(title = "Phone Use Purposes", x = "purpose", y= "Count") + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) 

# bar chart 2: Count of phone usage by intention 
ggplot(latest_data, aes(x = intention)) + 
  geom_bar(fill= "purple") + labs (title = "Phone Use Intentions", x = "intention", y= "Count") 
```